\chapter{NodeJS}
"As an asynchronous event driven framework, Node.js is designed to build scalable network applications. 
Node is similar in design to and influenced by systems like Ruby's Event Machine or Python's Twisted. 
Node takes the event model a bit further, it presents the event loop as a language construct instead of as a library." \cite{nodejsabout}

"Node.js is considered by many as a game-changer—the biggest shift of the decade in web development.[...]\\
 First, Node.js applications are written in JavaScript, the language of the web, the only programming language supported natively by a majority of web browsers. [...]\\
The second revolutionizing factor is its single-threaded, asynchronous architecture. 
Besides obvious advantages from a performance and scalability point of view, this characteristic changed the way developers approach concurrency and parallelism. [...]\\
The last and most important aspect of Node.js lies in its ecosystem: the npm package manager, its constantly growing database of modules, its enthusiastic and helpful community, and most importantly, its very own culture based on simplicity, pragmatism, and extreme modularity. "\cite{nodejsbook}

"JavaScript (JS) is a lightweight, interpreted, programming language with first-class functions. Most well-known as the scripting language for Web pages, many non-browser environments use it such as node.js and Apache CouchDB. JS is a prototype-based, multi-paradigm, dynamic scripting language, supporting object-oriented, imperative, and functional programming styles."\cite{mozillaJS}

\paragraph{Non blocking I/O}
A set of bindings responsible for wrapping and exposing libuv and other low-level functionality to JavaScript.\cite{nodejsbook}

Non blocking I/O in NodeJS is provided by libuv\cite{nodejsabout}\cite{nodejsbook}. 
Which is "libuv is a multi-platform support library with a focus on asynchronous I/O. It was primarily developed for use by Node.js, but it’s also used by Luvit, Julia, pyuv, and others."\cite{libuv}\\
libuv properties\cite{libuvBasic}:
\begin{itemize}
\item Abstract operations, not events
\item Support different nonblocking I/O models
\item Focus on embeddability and perfomace
\end{itemize}


\paragraph{Node core}
A core JavaScript library (called node-core) that implements the high-level Node.js API.

\paragraph{V8/Chakra} the JavaScript engine originally developed by Google for the Chrome browser/ Microsoft for IE 9 browser"\cite{nodejsbook} 

\paragraph{Event handling}
NodeJS asynchronous nature provided by event handler which is an implementation of reactor pattern. Here is the description of process lifecycle\cite{nodejsbook}:
\begin{enumerate}
\item The application generates a new I/O operation by submitting a request to the Event Demultiplexer. The application also specifies a handler, which will be invoked when the operation completes. Submitting a new request to the Event Demultiplexer is a non-blocking call and it immediately returns the control back to the application.
\item When a set of I/O operations completes, the Event Demultiplexer pushes the new events into the Event Queue.
\item At this point, the Event Loop iterates over the items of the Event Queue.
\item For each event, the associated handler is invoked.
\item The handler, which is part of the application code, will give back the control to the Event Loop when its execution completes. However, new asynchronous operations might be requested during the execution of the handler, causing new operations to be inserted in the Event Demultiplexer, before the control is given back to the Event Loop.
\item When all the items in the Event Queue are processed, the loop will block again on the Event Demultiplexer which will then trigger another cycle.
\end{enumerate}

\paragraph{Approaches for asynchronous information flow handling}
\begin{itemize}
	\item \textit{Continuation Passing.} Definition and call of a function within function which performs asynchronous operation
	\item \textit{Callbacks.} Passing as last input parameter function with specific signature for iinput paramteres (error, data), which performs operation/error handling over returned data after it was obtained.
	\item \textit{Async.} JavaScript library which gives an opportunity to write asynchronous functions execution in chain or parallel form within single information flow.
	\item \textit{Promises.} Function can return promise object with can be resolved or rejected in a later time when it particular method will be called by other function.
	\item\textit{Streams.} Piping asynchronous functions one to another. Result of first will be pushed to next stream whenever it is available, or pulled by the next stream whenever it is necessary (depends from stream mode)
	\item\textit{Generators.} Type of constructor introduced in ECMA6 which returns iterator value. Which will iterate through the code unless it will rich yeild method which will wait for return value without blocking event loop.

\end{itemize}
